A comparison of two second order traffic flow models

### 2015-03-13 FirstDraftMaterials/Draft.tex
Added clawpack figures

\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{subfigure}
\usepackage{enumerate}

@@

\begin{figure}[h!]
 \centering
 \subfigure[Hugonio loci for $\lambda_1$ and $\lambda_2$ shown in magenta and red, respectively.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_Loci.jpg}
   }
 \subfigure[Integral curves for $\lambda_1$, $\lambda_2$ shown in light and dark green, respectively.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_IntegralCurves.jpg}
   }
 \subfigure[$\lambda_1$ loci and integral curve passing through
  a point $(\rho_*, v_*)$, with $\lambda_1$ contour lines shown in cyan.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_Lambda1Curves.jpg}
   }
    \subfigure[$\lambda_2$ loci and integral curve passing through
  a point $(\rho_*, v_*)$, with $\lambda_2$ contour lines shown in cyan.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_Lambda2Curves.jpg}
   }
 \subfigure[Valid curves for a point $q_l$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_validStateCurvesLeft.jpg}
   }
 \subfigure[Valid curves for a point $q_r$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_validStateCurvesRight.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$ in the $M = (\rho, \rho v)$ plane. Note that loci are shown in red and magenta and integral curves are shown in green.}
  \label{fig:PW_curves}
\end{figure}

@@

\begin{figure}[h!]
 \centering
 \subfigure[$\lambda_1$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the U plane passing through
  the point $(\rho_*, v_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U.jpg}
   }
    \subfigure[$\lambda_1$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the M plane passing through 
 the point $(\rho_*,m_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M.jpg}
   }
       \subfigure[$\lambda_1$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the Y plane passing through 
 the point $(\rho_*, y_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$ 
 in each of the different planes. Since the loci and integral curves coincide, they are 
 both simply called the ``curves'' in the captions of the above figures. 
 Figures (c), (f), (i) show both curves for a given point in each plane.}
  \label{fig:AR_curves}
\end{figure}

@@

\begin{figure}[h!]
 \centering
 \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U.jpg}
   }
    \subfigure[Valid waves for the point $q_l$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_ql.jpg}
   }
    \subfigure[Valid waves for the point $q_r$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_qr.jpg}
   }
    \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M.jpg}
   }
 \subfigure[Valid waves for the point $q_l$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_ql.jpg}
   }
 \subfigure[Valid waves for the point $q_r$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_qr.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures showing the calculation of the valid waves for a given point. Figures (a)
  and (d) show the $\lambda_1$ curves in black with the $\lambda_1$ contours 
  in cyan. The other figures show valid shocks in red and valid rarefaction 
  waves in green. The contact discontinuity is shown in blue.}
   \label{fig:AR_validity}
\end{figure}

@@

\begin{figure}[h!]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example1.jpg}
   }
    \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/PW_example1.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 from the AR and PW models.}
  \label{fig:example1}
\end{figure}

\begin{figure}[h!]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example2.jpg}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/PW_example2.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 from the AR and PW models.}
  \label{fig:example2}
\end{figure}

@@

>>>>

\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{float}

@@

\begin{figure}[H]
 \centering
 \subfigure[Hugonio loci for $\lambda_1$ and $\lambda_2$ shown in magenta and red, respectively.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_Loci.jpg}
   }
 \subfigure[Integral curves for $\lambda_1$, $\lambda_2$ shown in light and dark green, respectively.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_IntegralCurves.jpg}
   }
 \subfigure[$\lambda_1$ loci and integral curve passing through
  a point $(\rho_*, v_*)$, with $\lambda_1$ contour lines shown in cyan.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_Lambda1Curves.jpg}
   }
    \subfigure[$\lambda_2$ loci and integral curve passing through
  a point $(\rho_*, v_*)$, with $\lambda_2$ contour lines shown in cyan.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_Lambda2Curves.jpg}
   }
 \subfigure[Valid curves for a point $q_l$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_validStateCurvesLeft.jpg}
   }
 \subfigure[Valid curves for a point $q_r$.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/PW_validStateCurvesRight.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$ in the $M = (\rho, \rho v)$ plane. Note that loci are shown in red and magenta and integral curves are shown in green.}
  \label{fig:PW_curves}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \subfigure[$\lambda_1$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the U plane passing through
  the point $(\rho_*, v_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_U.jpg}
   }
    \subfigure[$\lambda_1$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the M plane passing through 
 the point $(\rho_*,m_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_M.jpg}
   }
       \subfigure[$\lambda_1$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb1.jpg}
   }
 \subfigure[$\lambda_2$-curves in the Y plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y_lamb2.jpg}
   }
 \subfigure[$\lambda_1$-curve and $\lambda_2$-curve in the Y plane passing through 
 the point $(\rho_*, y_*)$ denoted by the red point.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/HLIC_Y.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures of the Hugonio loci and integral curves for $\lambda_1$ and $\lambda_2$ 
 in each of the different planes. Since the loci and integral curves coincide, they are 
 both simply called the ``curves'' in the captions of the above figures. 
 Figures (c), (f), (i) show both curves for a given point in each plane.}
  \label{fig:AR_curves}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U.jpg}
   }
    \subfigure[Valid waves for the point $q_l$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_ql.jpg}
   }
    \subfigure[Valid waves for the point $q_r$ in the U plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_U_qr.jpg}
   }
    \subfigure[$\lambda_1$-curves with contours of $\lambda_1$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M.jpg}
   }
 \subfigure[Valid waves for the point $q_l$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_ql.jpg}
   }
 \subfigure[Valid waves for the point $q_r$ in the M plane.]{
  \includegraphics[width=45mm]{../MatlabCode/Images/Validity_M_qr.jpg}
   }
 \caption[Optional caption for list of figures]
 {Figures showing the calculation of the valid waves for a given point. Figures (a)
  and (d) show the $\lambda_1$ curves in black with the $\lambda_1$ contours 
  in cyan. The other figures show valid shocks in red and valid rarefaction 
  waves in green. The contact discontinuity is shown in blue.}
   \label{fig:AR_validity}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example1.jpg}
   }
    \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/PW_example1.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 from the AR and PW models.}
  \label{fig:example1}
\end{figure}

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/AR_example2.jpg}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../MatlabCode/Images/PW_example2.jpg}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 from the AR and PW models.}
  \label{fig:example2}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../ClawpackCode/AR/ARexample1.png}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../ClawpackCode/PW/PWexample1.png}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 1 computed in Clawpack.}
  \label{fig:example2}
\end{figure}

\begin{figure}[H]
 \centering
 \subfigure[Solution from the AR model.]{
  \includegraphics[width=70mm]{../ClawpackCode/AR/ARexample2.png}
   }
 \subfigure[Solution from the PW model.]{
  \includegraphics[width=70mm]{../ClawpackCode/PW/PWexample2.png}
   }
 \caption[Optional caption for list of figures]
 {Solutions to the Riemann problem for example 2 computed in Clawpack.}
  \label{fig:example2}
\end{figure}
